00-OD-preparation

### 2022-05-23 00-OD-preparation.Rmd
Created an additional .Rmd exploring 1) trip chained trips, 2) spatial availability calcs, 3) mode shifting due to LEZ

Importing a list of all the municipalities within the Madrid region and adding them to the zone shape file:
```{r}
t <- read_excel("data-raw/ZonificacionZT1259 complete.xlsx") %>% select(ZT1259, Municipality)

@@

Let's see how long are short-trips are (by distance, assuming in km units):
```{r}
t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE <= 60) %>% select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t)
```

As you can see though there are some long distance trip (greater than 60km). There are 101 trips which are between 60km to 600km and 1 trip greater than 600km. For perspective though, these trips make up onl 0.3% of total trips taken ( ~100 trips out of ~28,000 trips).
```{r}
t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE >= 60 & DISTANCIA_VIAJE <= 600) %>% select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t, breaks = 50)

t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE >= 600) %>% select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t, breaks = 50)
```

>>>>

Importing a list of all the municipalities within the Madrid region and adding them to the zone shape file:
```{r}
t <- read_excel("data-raw/ZonificacionZT1259 complete.xlsx") %>% dplyr::select(ZT1259, Municipality)

@@

Let's see how long are short-trips are (by distance, assuming in km units):
```{r}
t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE <= 60) %>% dplyr::select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t)
```

As you can see though there are some long distance trip (greater than 60km). There are 101 trips which are between 60km to 600km and 1 trip greater than 600km. For perspective though, these trips make up onl 0.3% of total trips taken ( ~100 trips out of ~28,000 trips).
```{r}
t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE >= 60 & DISTANCIA_VIAJE <= 600) %>% dplyr::select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t, breaks = 50)

t <- OD_v_Oc_Dt %>% filter(DISTANCIA_VIAJE >= 600) %>% dplyr::select(DISTANCIA_VIAJE) %>% unlist() %>% as.numeric() 
hist(t, breaks = 50)
```
